---
name: Calvin He
date: "`r format(Sys.time(), '%B, %Y')`"
position: "Research Economist"
address: "65 Martin Place, Sydney NSW 2000, Australia"
email: "calvin.y.he@gmail.com"
phone: +61 490 779 547
headcolor: 414141
output: 
  vitae::moderncv:
    theme: banking
    # vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education
```{r education}
library(tibble)
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "University Medal and First Class honours; WAM: 92.33",
  "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "Honours thesis: Sovereign Default Risk and the Fiscal Spending Multiplier",
    "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "Supervisors: Richard Holden, Mariano Kulish and James Morley",
  "BEc/Com in Economics, Econometrics and Finance", "University of New South Wales", "Australia", "2012 - 2015", "WAM: 89.11",
  "BEc (International exchange)", "University of California, Los Angeles", "USA", "Jan. - Jun. 2014", "GPA: 3.96",
  "High School Certificate", "Sydney Technical High School", "Australia", "2006 - 2011", "ATAR: 99.35"
) %>% 
  detailed_entries(with = degree, dates, what = uni, loc, details)
```

# Work experience
```{r work experience}
tribble(
  ~ dates, ~ position, ~ organisation, ~ details,
  "May 2018 - present", "Research Economist", "Reserve Bank of Australia", "I work in the Reserve Bank's Economic Research department. I undertake longer-term research on the Australian economy and monetary policy.",
  "May 2018 - present", "Research Economist", "Reserve Bank of Australia", "Research focus: monetary policy shocks and identification, heterogeneous effects of monetary policy, firm productivity and life-cycle, forecasting methods, and macrofinancial linkages.",
  "Feb. 2017 - May 2018", "Fixed Income Analyst", "Reserve Bank of Australia", "I worked in the Reserve Bank's Domestic Markets department, analysing fixed income activity in Australia or by Australian companies. This included daily monitoring of bond and derivative markets and longer-term analytical work on trends in securities pricing, issuance, and turnover.",
  "Mar. 2016 - Oct. 2016", "Tutor-in-charge", "University of New South Wales - School of Economics", "Managed a course with over 1,000 students and a team of over 20 tutors.",
  "Mar. 2016 - Oct. 2016", "Tutor-in-charge", "University of New South Wales - School of Economics", "Awarded the 2016 UNSW Business School Excellence in Tutoring Award.",
   "Mar. 2015 - present", "Tutor/Demonstrator", "University of New South Wales - School of Economics", "Tutor for Microeconomics 1 (Econ1101) - 2015 (S1 and S2), 2016 (S1 and S2), 2019 (T1 and T2)."
  
) %>% 
  detailed_entries(
    with = position, 
    when = dates,
    what = organisation,
    why  = details
  )
```

# Research and presentations
1. Distributional Consequences of Monetary Policy: Evidence from Local Housing Markets with [Gianni La Cava](https://www.linkedin.com/in/gianni-la-cava-55271a35?originalSubdomain=au) (RBA RDP forthcoming)
    * Presented at: [Australian Conference of Economists (ACE) - Jul. 2019](https://www.ace2019.org.au/); RBA-RBNZ Workshop - Mar. 2019 
    * In the press: [The areas most vulnerable to interest rate changes](https://www.smh.com.au/business/the-economy/the-areas-most-vulnerable-to-interest-rate-changes-20190715-p527gf.html)
2. Holding Productivity Accountable: The role of business dynamics in productivity growth
    * Presented at: [Economic Measurement Group Workshop - Nov. 2018](https://www.business.unsw.edu.au/research-site/centreforappliedeconomicresearch-site/Documents/emg2018-3_CHe_Holding-Productivity-Accountable-UNSW-EMG-Workshop.pdf)
3.  Housing Wealth Effects: The Long View [(Guren, McKay, Nakamura, Steinsson 2018)](https://www.nber.org/papers/w24729) (an Australian replication)
    * Presented at: Sydney Macroeconomic Reading Group - Apr. 2019 

# Skills
```{r skills}
tribble(
  ~dates, ~role,
  "Programming", "R (preferred), SQL, Matlab, STATA, EViews",
  "Software Development", "git, R package development, CI/CD, github, Team Foundation Server",
) %>% 
  brief_entries(when = dates, what= role)
```
<!-- # Work in Progress -->
# Awards and prizes
```{r awards}
tribble( ~ date, ~ award, ~details,
        "2016", "University Medal (Economics)", "UNSW",
        "2016", "UNSW Business School Excellence in Tutoring Award", "UNSW",
        "2016", "Herbert Smith Freehills Law and Economics Honours Scholarship", "UNSW",
        "2016", "UNSW Business School Honours Scholarship", "UNSW",
        "2016", "UNSW Honours Year Scholarship", "UNSW",
        "2012-15", "UNSW Business School Dean's Award", "UNSW",
        "2014", "Dean's Honor List", "UCLA",
        "2014", "Harry Manson Scholarship", "UNSW",
        "2014", "International Exchange Scholarship" , "UNSW", 
        "2011", "Premier's Award for All-Round Excellence", "NESA") %>% 
  brief_entries(what = award, when = date, with = details)
```
# Professional development
```{r professional development}
tribble(
  ~ dates, ~ course, ~ teacher,
  "May 2019", "Building Tidy Tools", "Instructor: Hadley Wickham",
  "Jul. 2018 ", "Monetary and Fiscal Policy with Heterogeneous Agents", "Instructor: Greg Kaplan"
) %>% 
 brief_entries(
    with = teacher, 
    when = dates,
    what = course
  )
```
# Other roles
```{r other_roles}
tribble(
  ~dates, ~role, ~ with,
  "2019", "Sydney Macroeconomic Reading Group coordinator", "Reserve Bank of Australia", 
  "2019", "RBA Conference Discussion editor", "Reserve Bank of Australia",
  "2019", "Public Education and Access ambassador", "Reserve Bank of Australia",
  "2019", "R User Group founder and coordinator", "Reserve Bank of Australia",
  "2018-19", "Internal seminar coordinator", "Reserve Bank of Australia"
) %>% 
  brief_entries(when = dates, what= role, with = with)

```

