---
name: Calvin He
date: "`r format(Sys.time(), '%B, %Y')`"
position: "PhD Student"
email: "calvinhe@stanford.edu"
phone: 
headcolor: 414141
output: 
  vitae::moderncv:
    theme: banking
    # vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education
```{r education}
library(tibble)
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Economics", "Stanford University", "USA", "2020-", "Fields (Planned): Macroeconomics and Finance",
  "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "University Medal and First Class honours; WAM: 92.33",
  "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "Honours thesis: Sovereign Default Risk and the Fiscal Spending Multiplier",
    "BEc (Hons) in Economics", "University of New South Wales", "Australia", "2016", "Supervisors: Richard Holden, Mariano Kulish and James Morley",
  "BEc/Com in Economics, Econometrics and Finance", "University of New South Wales", "Australia", "2012 - 2015", "WAM: 89.11",
  "BEc (International exchange)", "University of California, Los Angeles", "USA", "Jan. - Jun. 2014", "GPA: 3.96"
) %>% 
  detailed_entries(with = degree, dates, what = uni, loc, details)
```

# Work experience
```{r work experience}
tribble(
  ~ dates, ~ position, ~ organisation, ~ details,
  "May 2018 - Aug. 2021", "Research Economist", "Reserve Bank of Australia", "I undertake longer-term research on the Australian economy and monetary policy.",
  "May 2018 - Aug. 2021", "Research Economist", "Reserve Bank of Australia", "Research focus: monetary policy shocks and identification, heterogeneous effects of monetary policy, housing market dynamics, firm productivity and life-cycle, forecasting methods, and macrofinancial linkages.",
  "Feb. 2017 - May 2018", "Fixed Income Analyst", "Reserve Bank of Australia", "I worked in the Reserve Bank's Domestic Markets department, analysing fixed income activity in Australia or by Australian companies. This included daily monitoring of bond and derivative markets, and analytical work on long-term trends and relationships in securities pricing, issuance, and turnover.",
  "Feb. 2016 - Oct. 2016", "Tutor-in-charge", "University of New South Wales - School of Economics", "Managed a course with over 1,000 students and a team of over 20 tutors.",
  "Feb. 2016 - Oct. 2016", "Tutor-in-charge", "University of New South Wales - School of Economics", "Awarded the 2016 UNSW Business School Excellence in Tutoring Award.",
   "Mar. 2015 - Jun. 2020", "Tutor/Demonstrator", "University of New South Wales - School of Economics", "Tutor for Microeconomics 1 (Econ1101) - 2015 (S1 and S2), 2016 (S1 and S2), 2019 (T1 and T2).",
     "Mar. 2015 - Jun. 2020", "Tutor (Teaching Assistant)", "University of New South Wales - School of Economics", "Student satisfaction: 92%."
  
) %>% 
  detailed_entries(
    with = position, 
    when = dates,
    what = organisation,
    why  = details
  )
```

# Research and presentations
1. Monetary Policy, Equity Markets and the Information Effect ([\textcolor{blue}{RBA Research Discussion Paper 2021-04)}](https://www.rba.gov.au/publications/rdp/2021/2021-04.html))

\quad \textit{Abstract: Central banks analyse copious amounts of information to assess the economic outlook to then set monetary policy. So, could changes in monetary policy reveal some additional information about the economic outlook to the public? This channel is known as the ‘information effect’. The information effect posits that, in addition to the usual effects of monetary policy, agents interpret an interest rate increase as signalling some additional positive economic information. This effect, if strong enough, could then lead to dynamics where an increase in interest rates causes an expansion in economic activity.}\par
\quad \textit{I evaluate whether the information effect can be detected in Australia through the lens of equity markets. I find that, contrary to the predictions of the information effect, a surprise monetary tightening from a monetary policy announcement causes equity prices to fall. I also show that this response in equity prices is, at least in part, driven by downward adjustments in expected earnings growth. These responses are consistent with conventional views of the effects of monetary policy. However, looking beyond monetary policy announcements yields some evidence that an information effect could be present through other forms of Reserve Bank of Australia (RBA) communication. I find speeches delivered by the RBA Governor generate responses in equity prices and earnings forecasts consistent with the information effect. But this result appears to be the exception rather than the rule. For most monetary policy communication, at least in equity markets, the information effect is not an important channel of monetary policy.}

2. The Distributional Effects of Monetary Policy: Evidence from Local Housing Markets with [Gianni La Cava](https://www.linkedin.com/in/gianni-la-cava-55271a35?originalSubdomain=au) ([\textcolor{blue}{RBA Research Discussion Paper 2020-02}](https://www.rba.gov.au/publications/rdp/2020/2020-02.html))
    * Presented at: [Australian Conference of Economists (ACE) - Jul. 2019](https://www.ace2019.org.au/); RBA-RBNZ Workshop - Mar. 2019 
    * In the press: [The areas most vulnerable to interest rate changes](https://www.smh.com.au/business/the-economy/the-areas-most-vulnerable-to-interest-rate-changes-20190715-p527gf.html)
  
\quad \textit{Abstract: We document that the effect of monetary policy on housing prices varies substantially by local housing market. We show that this heterogeneity across local housing markets can be partly explained by variation in housing supply conditions – housing prices are typically more sensitive to changes in interest rates in areas where land is more expensive. But other factors are important too. Specifically, we find the sensitivity is greater in areas where incomes are relatively high, households are more indebted and there are more investors. Taken together, this suggests that the state of the economy can affect the sensitivity of housing prices to monetary policy. We also directly explore how monetary policy affects housing wealth inequality. We find that housing prices in more expensive areas are more sensitive to changes in interest rates than in cheaper areas. This suggests that lower interest rates increase housing wealth inequality, while higher rates do the opposite. However, these effects appear to be temporary.}
   
3. Holding Productivity Accountable: The role of business dynamics in productivity growth
    * Presented at: [Economic Measurement Group Workshop - Nov. 2018](https://www.business.unsw.edu.au/research-site/centreforappliedeconomicresearch-site/Documents/emg2018-3_CHe_Holding-Productivity-Accountable-UNSW-EMG-Workshop.pdf)
4.  Housing Wealth Effects: The Long View [(Guren, McKay, Nakamura, Steinsson 2018)](https://www.nber.org/papers/w24729) (an Australian replication)
    * Presented at: Sydney Macroeconomic Reading Group - Apr. 2019 

# Skills
```{r skills}
tribble(
  ~dates, ~role,
  "Programming", "R (preferred), SQL, Matlab, STATA, EViews",
  "Software Development", "git, R package development, CI/CD, github, Azure DevOps",
) %>% 
  brief_entries(when = dates, what= role)
```
<!-- # Work in Progress -->
# Awards and prizes
```{r awards}
tribble( ~ date, ~ award, ~details,
        "2020", "Governor's Award of Excellence", "RBA",
        "2016", "University Medal (Economics)", "UNSW",
        "2016", "First Class Honours (Economics)", "UNSW",
        "2016", "UNSW Business School Excellence in Tutoring Award", "UNSW",
        "2016", "Herbert Smith Freehills Law and Economics Honours Scholarship", "UNSW",
        "2016", "UNSW Business School Honours Scholarship", "UNSW",
        "2016", "UNSW Honours Year Scholarship", "UNSW",
        "2012-15", "UNSW Business School Dean's Award", "UNSW",
        "2014", "Dean's Honor List", "UCLA",
        "2014", "Harry Manson Scholarship", "UNSW",
        "2014", "International Exchange Scholarship" , "UNSW", 
        "2011", "Premier's Award for All-Round Excellence", "NESA") %>% 
  brief_entries(what = award, when = date, with = details)
```
# Professional development
```{r professional development}
tribble(
  ~ dates, ~ course, ~ teacher,
  "May 2019", "Building Tidy Tools", "Instructor: Hadley Wickham",
  "Jul. 2018 ", "Monetary and Fiscal Policy with Heterogeneous Agents", "Instructor: Greg Kaplan"
) %>% 
 brief_entries(
    with = teacher, 
    when = dates,
    what = course
  )
```
# Other roles
```{r other_roles}
tribble(
  ~dates, ~role, ~ with,
  "2019-21", "Sydney Macroeconomic Reading Group coordinator", "Reserve Bank of Australia", 
  "2019", "RBA Conference Discussion editor", "Reserve Bank of Australia",
  "2019", "Public Education and Access ambassador", "Reserve Bank of Australia",
  "2019", "R User Group founder and coordinator", "Reserve Bank of Australia",
  "2019", "Aboriginal and Indigenous Employee Resource Group member",  "Reserve Bank of Australia",
  "2018-19", "Internal seminar coordinator", "Reserve Bank of Australia",
  "2018-19", "Summer intern supervisor", "Reserve Bank of Australia",
  "2018", "Career Trackers Indigenous intern  supervisor", "Reserve Bank of Australia",
  "2014-15", "UNSW Policy Society founder and president", "UNSW",
  "2013", "180 Degrees consultant", "UNSW"
) %>% 
  brief_entries(when = dates, what= role, with = with)

```

