%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{414141}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=52pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...



% personal data
\name{}{Calvin He}
\title{Research Economist}
\address{65 Martin Place, Sydney NSW 2000, Australia}{}{}
\phone[mobile]{+61 490 779 547} % Phone number
\email{\donothing{\href{mailto:calvin.y.he@gmail.com}{\nolinkurl{calvin.y.he@gmail.com}}}}
 % Personal website



% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{
	\cventry{#2}{#1}{#3}{#4}{}{{\ifx#5\empty\else{\begin{itemize}#5\end{itemize}}\fi}}}
\def\detailedsection#1{\nopagebreak#1}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvitem{#2}{#1. #3}}
\def\briefsection#1{\nopagebreak#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypertarget{education}{%
\section{Education}\label{education}}

\detailedsection{\detaileditem{University of New South Wales}{2016}{BEc (Hons) in Economics}{Australia}{\item{University Medal and First Class honours; WAM: 92.33}\item{Honours thesis: Sovereign Default Risk and the Fiscal Spending Multiplier}\item{Supervisors: Richard Holden, Mariano Kulish and James Morley}}\detaileditem{University of New South Wales}{2012 - 2015}{BEc/Com in Economics, Econometrics and Finance}{Australia}{\item{WAM: 89.11}}\detaileditem{University of California, Los Angeles}{Jan. - Jun. 2014}{BEc (International exchange)}{USA}{\item{GPA: 3.96}}\detaileditem{Sydney Technical High School}{2006 - 2011}{Higher School Certificate}{Australia}{\item{ATAR: 99.35}}}

\hypertarget{work-experience}{%
\section{Work experience}\label{work-experience}}

\detailedsection{\detaileditem{Reserve Bank of Australia}{May 2018 - present}{Research Economist}{}{\item{I work in the Reserve Bank's Economic Research department. I undertake longer-term research on the Australian economy and monetary policy.}\item{Research focus: monetary policy shocks and identification, heterogeneous effects of monetary policy, housing market dynamics, firm productivity and life-cycle, forecasting methods, and macrofinancial linkages.}}\detaileditem{Reserve Bank of Australia}{Feb. 2017 - May 2018}{Fixed Income Analyst}{}{\item{I worked in the Reserve Bank's Domestic Markets department, analysing fixed income activity in Australia or by Australian companies. This included daily monitoring of bond and derivative markets and analytical work on long-term trends and relationships in securities pricing, issuance, and turnover.}}\detaileditem{University of New South Wales - School of Economics}{Feb. 2016 - Oct. 2016}{Tutor-in-Charge}{}{\item{Managed a course with over 1,000 students and a team of over 20 tutors.}\item{Awarded the 2016 UNSW Business School Excellence in Tutoring Award.}}\detaileditem{University of New South Wales - School of Economics}{Mar. 2015 - present}{Tutor/Demonstrator}{}{\item{Tutor for Microeconomics 1 (Econ1101) - 2015 (S1 and S2), 2016 (S1 and S2), 2019 (T1 and T2).}\item{Student satisfaction: 92\%.}}}

\hypertarget{research-and-presentations}{%
\section{Research and presentations}\label{research-and-presentations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Distributional Consequences of Monetary Policy: Evidence from Local Housing Markets with \href{https://www.linkedin.com/in/gianni-la-cava-55271a35?originalSubdomain=au}{Gianni La Cava} (RBA RDP forthcoming)

  \begin{itemize}
  \tightlist
  \item
    Presented at: \href{https://www.ace2019.org.au/}{Australian Conference of Economists (ACE) - Jul.~2019}; RBA-RBNZ Workshop - Mar.~2019
  \item
    In the press: \href{https://www.smh.com.au/business/the-economy/the-areas-most-vulnerable-to-interest-rate-changes-20190715-p527gf.html}{The areas most vulnerable to interest rate changes}
  \end{itemize}
\item
  Holding Productivity Accountable: The role of business dynamics in productivity growth

  \begin{itemize}
  \tightlist
  \item
    Presented at: \href{https://www.business.unsw.edu.au/research-site/centreforappliedeconomicresearch-site/Documents/emg2018-3_CHe_Holding-Productivity-Accountable-UNSW-EMG-Workshop.pdf}{Economic Measurement Group Workshop - Nov.~2018}
  \end{itemize}
\item
  Housing Wealth Effects: The Long View \href{https://www.nber.org/papers/w24729}{(Guren, McKay, Nakamura, Steinsson 2018)} (an Australian replication)

  \begin{itemize}
  \tightlist
  \item
    Presented at: Sydney Macroeconomic Reading Group - Apr.~2019
  \end{itemize}
\end{enumerate}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\briefsection{\briefitem{R (preferred), SQL, Matlab, STATA, EViews}{Programming}{}\briefitem{git, R package development, CI/CD, github, Team Foundation Server}{Software Development}{}}

\hypertarget{awards-and-prizes}{%
\section{Awards and prizes}\label{awards-and-prizes}}

\briefsection{\briefitem{University Medal (Economics)}{2016}{UNSW}\briefitem{UNSW Business School Excellence in Tutoring Award}{2016}{UNSW}\briefitem{Herbert Smith Freehills Law and Economics Honours Scholarship}{2016}{UNSW}\briefitem{UNSW Business School Honours Scholarship}{2016}{UNSW}\briefitem{UNSW Honours Year Scholarship}{2016}{UNSW}\briefitem{UNSW Business School Dean's Award}{2012-15}{UNSW}\briefitem{Dean's Honor List}{2014}{UCLA}\briefitem{Harry Manson Scholarship}{2014}{UNSW}\briefitem{International Exchange Scholarship}{2014}{UNSW}\briefitem{Premier's Award for All-Round Excellence}{2011}{NESA}}

\hypertarget{professional-development}{%
\section{Professional development}\label{professional-development}}

\briefsection{\briefitem{Building Tidy Tools}{May 2019}{Instructor: Hadley Wickham}\briefitem{Monetary and Fiscal Policy with Heterogeneous Agents}{Jul. 2018 }{Instructor: Greg Kaplan}}

\hypertarget{other-roles}{%
\section{Other roles}\label{other-roles}}

\briefsection{\briefitem{Sydney Macroeconomic Reading Group coordinator}{2019}{Reserve Bank of Australia}\briefitem{RBA Conference Discussion editor}{2019}{Reserve Bank of Australia}\briefitem{Public Education and Access ambassador}{2019}{Reserve Bank of Australia}\briefitem{R User Group founder and coordinator}{2019}{Reserve Bank of Australia}\briefitem{Internal seminar coordinator}{2018-19}{Reserve Bank of Australia}}


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
